%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experiences}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %---------------------------------------------------------
  \cventry
  {Independent Software Engineer (Contract)} % Job title
  {Self-employed (Remote)} % Organization
  {Toronto, ON, Canada} % Location
  {Sep. 2024 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed a lightweight Angular-based dashboard for real-time sensor monitoring, prioritizing clarity and responsiveness over unnecessary tooling complexity.}
      \item {Enabled fully dynamic DOCX form generation where user input could safely expand tables or wrap across multiple lines without breaking layout or styles, turning rigid templates into data-driven documents suitable for real-world form submissions.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Web Development Engineer} % Job title
  {Duotify Inc.} % Organization
  {Taipei, Taiwan} % Location
  {Jun. 2020 - Jan. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Identified performance bottlenecks caused by ORM-based data transformation and intentionally shifted critical reporting logic to SQL Server stored procedures, trading abstraction for performance and predictability, reducing execution time from 3 minutes to 4 seconds while preserving data integrity.}
      \item {Designed and delivered 3 backend API services with CI/CD pipelines, balancing deployment speed and release stability by standardizing build and deployment workflows, reducing setup time by 30 minutes per release without increasing production risk.}
      \item {Evaluated trade-offs between cloud portability and delivery timelines when modifying 2 existing API services, establishing a lightweight AWS test environment (EC2, S3, RDS) and completing project handover 5 days ahead of schedule.}
      \item {Maintained and evolved 4 brownfield production platforms built on .NET across healthcare, finance, and biotech domains, delivering 10+ features through safe refactoring and incremental improvements while minimising operational risk.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {ERP Application Development Engineer} % Job title
  {Unitech Computer Co., Ltd.} % Organization
  {Taipei, Taiwan} % Location
  {Mar. 2019 - Jun. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked on legacy ASP.NET MVC 3 and AngularJS systems within brownfield B2B applications, developing a strong foundation in SQL Server–centric data modelling and query optimisation while maintaining production stability.}
      \item {Independently evaluated newer frontend approaches by prototyping a B2B platform using Angular 8, balancing modernization efforts against delivery risk in an enterprise environment.}
      \item {Resolved recurring production issues across internal and external systems by prioritizing correctness and maintainability over short-term fixes, establishing disciplined debugging and refactoring habits.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {InternShip} % Job title
  {SYSTEX UCOM Information Technology Co., Ltd.} % Organization
  {Taipei, Taiwan} % Location
  {Jul. 2018 - Mar. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Took ownership of a C\#-based module during an internship project, making implementation decisions and coordinating with teammates while working with ASP.NET WebForms and SQL Server, building an early understanding of stateful web architectures and long-term maintenance trade-offs.}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
